A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2019-01-13 article/03_Results.Rmd
some description of the simulation results

Simulation: What is to be expected in case of influence of spatial distance?

>>>>

The results of the simulation as presented in Figure \ref{simulation} confirm the expectation: In case of equal interaction intensity $I$ of separate populations, the correlation of cultural and spatial distance is weak (Figure \ref{simulation} A vs. C vs. E). It appears to be normally distributed around zero for many simulation runs, although individual runs can still yield remarkably high positive and negative correlation for certain time slots. The fluctuation of the correlation within one run can be strong and seems to increase for bigger values of $m_i$. If the interaction matrix $I$ is predefined to represent the spatial distance matrix (Figure \ref{simulation} BDF), then the mean correlation per time slot increases. The correlation increases as well with the degree of interaction $m_i$ (Figure \ref{simulation} D vs. F). Counterintuitively the fluctuation of the correlation is also here very high (Figure \ref{simulation} E vs. F). The correlation development observed for the variables *burial type* and *burial construction* fits to simulation runs in all presets, but becomes less likely if we assume $I$ to represent spatial distance and a high degree of interaction $m_i$ (Figure \ref{simulation} A vs. F). That's mostly because of the relatively strong negative correlation of cultural and spatial distance in the Middle and Late Bronze Age (1400 to 1000calBC).
